---
title: "Practical Machine learnin Course Project"
author: "Matías Alfonso"
date: "1 de febrero de 2018"
output: html_document
---
# Classe prediction model with Random Forest

## Summary
A Random Forest model was perform to predict the perfom in barbell lifts, correctly and incorrectly in 5 different ways. The accuracy of the model was 0.9984.

## Libraries and data
```{r init}
library(randomForest)
library(ggplot2)
library(caret)

# Download files
trainingURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"

if(!dir.exists("data")) dir.create("./data")

download.file(trainingURL, "./data/pml-training.csv")
download.file(testURL, "./data/pml-testing.csv")

## Read files
pml <- read.csv("./data/pml-training.csv")
validating <- read.csv("./data/pml-testing.csv")

# Create a building data set and validation set
set.seed(55493)
inTrain <- createDataPartition(y=pml$classe,
                               p=3/4, list=FALSE)
training <- pml[inTrain,]; testing <- pml[-inTrain,]

```

## Preprocess
The variables skewness, kurtosis, stddev, var, avg, max and min were discarded. A total of 57 variables ware preserved for the predictive model. 
```{r preprocess}
## PreProcess
## Selecting index variables
index <- grepl("skewness", names(training)) |
    grepl("kurtosis", names(training))  |
    grepl("stddev", names(training))  |
    grepl("var", names(training))  |
    grepl("avg", names(training))  |
    grepl("max", names(training))  |
    grepl("min", names(training)) |
    grepl("amplitude", names(training))

newTraining <- training[,!index]
newTraining <- newTraining[,-c(1,3,4)]

newTesting <- testing[,!index]
newTesting <- newTesting[, -c(1,3,4)]

## Converting to numerics
for (i in 2:56) {
    newTraining[,i] <- as.numeric(newTraining[,i])
}

for (i in 2:56) {
    newTesting[,i] <- as.numeric(newTesting[,i])
}
```

## fit Model
```{r randomForest}
fitMod <- randomForest(classe ~ ., method = "rf", data = newTraining, ntree = 300)
```

## Confusion Matrix
```{r confusionMatrix}
confusionMatrix(predict(fitMod, newTesting), newTesting$classe)
```
